tl20-05_berghei_pir_GeneSetEnrichmentQusage

### 2021-10-01 chapter3_results_bergheiPir/Manuscript_berghei_pir_GeneSetEnrichmentQusage.Rmd
Reverse order of labels and fix sub-fam order

order_path.names <- ordering(c('pirs', unique(pir_info$SorL), unique(pir_info$clade)), 
                             order_vector = c('pir','L','S'))

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i+1],'-',ordered_stages[i]) } }
    )
  ),
  'Liv.post48h-Liv.24h',
  'Asex.Schiz-Gam.Male',
  'Ook-Sporoz',
  'Gam.Male-Asex.Mixed',
  'Gam.Male-Liv.Meroz'
)

@@

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                r_order_vector),
                                       order(match(colnames(all_stats_df_cast), 
                                                   order_path.names))]

>>>>

order_path.names <- ordering(c('pirs', unique(pir_info$SorL), sort(unique(pir_info$clade))), 
                             order_vector = c('pir','L','S'))

@@

comparisons <- c(
  unlist(
    lapply(seq_along(ordered_stages),
           function(i){ if(i < length(ordered_stages)){ paste0(ordered_stages[i+1],'-',ordered_stages[i]) } }
    )
  ),
  'Liv.post48h-Liv.24h',
  'Gam.Male-Asex.Schiz',
  'Sporoz-Ook',
  'Gam.Male-Asex.Mixed',
  'Gam.Male-Liv.Meroz'
)

@@

all_stats_df_cast <- all_stats_df_cast[ordering(rownames(all_stats_df_cast),
                                                c(r_order_vector,
                                                  'Gam.Male-Asex.Mixed',
                                                  'Gam.Male-Liv.Meroz')),
                                                order(match(colnames(all_stats_df_cast), 
                                                            order_path.names))]
